Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
QA done on discussion

The generated C files from Cython used as Python bindings are not necessarily the most
optimized versions possible to write and they are ugly to read and change (from
a C perspective). However they are equal for all the \ac{SHA}-3 candidates
which means they should give the same performance penalty. The \ac{SHA}-256
version will of course not suffer from the same penalty. From
\autoref{tbl:cython:overhead} we can see the performance penalty of our
bindings, and we do believe better bindings can be made, also with the use of
Cython, but by someone with more skill and knowledge than us.

The alternative would be creating manual Python-bindings for all the candidates
which would require a lot more work on our side, especially given the lack of a
good enough and common \ac{API} for the implementations in \ac{SUPERCOP}.
Another fact important for this decision was that we did not know exactly which
implementation of each candidate we would end up using, and we ended up trying
several for most candidates.

\subsection{Faster implementations}
We do not claim to have tested the fastest possible nor existing version
of most of the candidates. We are certain that someone of more skill and
knowledge about the inner workings of the \ac{SHA}-3 candidates, \ac{GCC} and
Python could make significantly faster implementation.

\subsection{Test with different Erasure Coding schemes}
By default Tahoe-\ac{LAFS} comes with a coding scheme of 3-7-10 (shares needed,
shares happy, shares total) while we test with a configuration of 2-3-3. It
would have been interesting to see how this (and other schemes) would affect
both the overall performance and the percentage of time spent hashing.

\subsection{Measure with real use cases}
Our test use random generated data of a certain length. In a real use case for
Tahoe-\ac{LAFS} the data would probably be both of varying length, and of
lengths not tested by us. In a real use case both a feasible erasure coding
scheme would have to be decided, and the files would represent what you
actually would want to use Tahoe-\ac{LAFS} for.

\subsection{Truncate output from 512-bit implementations}
In our measurements and Python library we only consider 256-bit version of each
candidate. Some candidates does however have a faster implementation with
512-bit output. We could have used these implementations and truncated the
output to 256-bit, and possible achieved better results.

\subsection{Testing on difference architectures}
Our measurements are only done on a single computer with an 32-bit (x86)
system. It would have been possible to extend the survey to other
architectures, to see how this would affect the results.

>>>>

The generated C files from Cython used as Python bindings are not necessarily
the most optimized versions possible to write and they are difficult to read and
change from a C perspective. However, they are equal for all the \ac{SHA}-3
candidates, which means they should give the same performance penalty. The
\ac{SHA}-256 version will of course not suffer from this, as it is not written
using Cython. From \autoref{tbl:cython:overhead} we can see the performance
penalty of our bindings, and we do believe better bindings can be made, also
with the use of Cython, but by someone with more skill and knowledge than us.

The alternative would be to create manual Python bindings for all the
candidates, which would require a lot more work on our side, especially given
the lack of a good enough and common \ac{API} for the implementations in
\ac{SUPERCOP}

Another fact important for the decision on using Cython, was that we did not
know exactly which implementation of each candidate we would end up using.
Several implementations were tried out during testing, and this could only be
accomplished since we only had to do a minimal amount of work for each new
implementation test.

\subsection{Faster implementations}

We do not claim to have tested the fastest possible existing version
of most of the candidates. We are certain that someone of more skill and
knowledge about the inner workings of the \ac{SHA}-3 candidates, \ac{GCC} and
Python could make significantly faster implementations.

\subsection{Test with different Erasure Coding schemes}

By default, Tahoe-\ac{LAFS} comes with a coding scheme of 3-7-10 (shares needed,
shares happy, shares total) while we test with a configuration of 2-3-3. It
would have been interesting to see how this (and other schemes) would affect
both the overall performance and the percentage of time spent hashing.

\subsection{Measure with real use cases}

Our test use randomly generated data of a certain length. In a real use case for
Tahoe-\ac{LAFS}, the data would probably be both of varying length, and of
lengths not tested by us. Additionally, both a feasible erasure coding
scheme would have to be decided, and the files would represent what you actually
would want to use Tahoe-\ac{LAFS} for.

\subsection{Truncate output from 512-bit implementations}

In our measurements and in the created Python library, we only consider 256-bit version of each
candidate. Some candidates does however have a faster implementation with
512-bit output. We could have used these implementations and truncated the
output to 256-bit, and possible achieved better results.

\subsection{Testing on difference architectures}

Our measurements are only done on a single computer with an 32-bit (x86)
system. It would have been possible to extend the survey to other
architectures, to see how this would affect the results.
